Approximation as Differentiation: Notes

### 2025-05-25 main/category-of-families.tex
First pass over forward-mode AD.

The basic idea of (forward-mode) automatic differentiation, as first described by \citet{linnainmaa76}, was to
recognise that one could efficiently compute the pushforward map $\RR^m \to (\RR^m \linearto \RR^n)$ of a
differentiable function $f: \RR^m \to \RR^n$ alongside the computation of $f$ itself by defining a single map
$\tangents(f) = x \mapsto (f(x), \pushf{f}_x): \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$. Defining $f_1
= \pi_1 \comp f: \RR^m \to \RR^n$ and $f_2 = \pi_2 \comp f: \RR^m \to (\RR^m \linearto \RR^n)$, composition of
such maps can be expressed as:
\begin{align*}
(g \comp f)_1(x) &= f_1(g_1(x)) \\
(g \comp f)_2(x) &= g_2(f_1(x)) \comp f_2(x)
\end{align*}

>>>>

The basic idea of (forward-mode) automatic differentiation, as first described by \citet{linnainmaa76}, was to
recognise that one could efficiently compute the pushforward map $\pushf{f}: \RR^m \to (\RR^m \linearto
\RR^n)$ of a differentiable function $f: \RR^m \to \RR^n$ alongside the computation of $f$ itself by defining
a single map $\tangents(f) = x \mapsto (f(x), \pushf{f}_x): \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$.
Defining $f_1 = \pi_1 \comp f: \RR^m \to \RR^n$ and $f_2 = \pi_2 \comp f: \RR^m \to (\RR^m \linearto \RR^n)$,
composition of such maps can be expressed as:
\begin{align*}
(g \comp f)_1(x) &= f_1(g_1(x)) \\
(g \comp f)_2(x) &= g_2(f_1(x)) \comp f_2(x)
\end{align*}
